%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.3, 30 April 2017) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=2cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=0.5cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage{setspace}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Mulberry}{HTML}{031533}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{headingBlue}{HTML}{18499b}
\colorlet{heading}{headingBlue}
\colorlet{accent}{Mulberry}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{SlateGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\renewcommand{\baselinestretch}{1.3} 

%% sample.bib contains your publications
%\addbibresource{sample.bib}

\begin{document}
\name{Emil Sebastian Rømer}
\tagline{Software Engineer at Ramboll Denmark \& M.Sc. Software Engineering }
%\photo{2.8cm}{images/migsdu}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{emilromer@hotmail.com}
  \phone{+45 3024 5719}
  \mailaddress{Vesterbro 59, st, 5000 Odense C}
  \location{Denmark}
%  \homepage{www.linkedin.com/in/romeren/}
%  \twitter{@twitterhandle}
  \linkedin{https://www.linkedin.com/in/romeren/}
%  \github{github.com/yourid}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want. 

\makecvheader

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.



\cvsection{Application: Software Engineers specialized in JAVA}
\vspace{5mm}
Hi Universal Robots.
\\
\vspace{5mm}
It is with great excitement that I submit my application for the \textit{Software Engineers specialized in JAVA} position.
\\
\vspace{5mm}
I am a graduate within Software Engineering and with great interest in robotics, IoT and automation.
With my line of study I have had a focus on generating value for both company and customer, with semester projects in collaboration with different businesses.   
\\

During my studies I have taken the following highly-relevant courses for the position you describe:
\vspace{2mm} 
\begin{itemize}
	\item Advanced Software Systems Design and Technologies
	\item Component-Based Software Development
	\item Domain Specific Languages
	\item Embedded Systems with Linux
	\item Software Maintenance
	\item Software Customization and
	\item User Centered Design
\end{itemize}
\vspace{5mm} 
With these competences, you will find me highly qualified for developing quality software with the entire software life-cycle in focus.
For instance, in software- maintenance and customization I have learned how to develop software systems that do not have an exponential cost associated with maintenance and continuous development.
Further, I have learned about and worked with a great variety of frameworks for dividing software into components (including OSGi and Swing) as well as a set of service architectures.
\\
\vspace{5mm} 
The position also requires the ability to achieve quality through Test-Driven development.
In my studies, I have worked with Test-Driven development both in the form of top-down and bottom-up approaches to achieve BDD, ATDD and TDD.
In addition, I have worked with benchmarking development performance based on KPIs derived from these development strategies to quantify and control the quality of the developed software.
\\
\vspace{5mm} 
I have worked with continuous integration and continuous deployment, during my work at both Powel Denmark and at Ramboll, in order to achieve faster development cycles and early acceptance-test verifications.
Thus, I fully understand the need for revision control systems when working with these practices and I have experience working with SVN, TFS and I am a heavy user of GIT.

\vspace{5mm} 
Thank you in advance for the time you dedicated to my application. I am looking forward to hearing from you.


\vspace{5mm}
Best regards,\\
\cvsubsection{Emil Sebastian Rømer}

\end{document}
