\cvsection{Projects}

\cvachievement{\faWifi}{Occupancy detection}{As a RnD project at the institute for Energy Informatics, i worked on building portable devices for occupancy detection. The prototype devices was build on ATMega328P processors on a custom cirtuit from my own design. In this project we used a RN41 bluetooth modules to sniff on traffic from other devices. The hipothesis here was that with a network of multiple of theses portable devices, it would be possible to either triangulate or fingerprint locations of occupancs, with a higher accuacy than GPS tracking in a indoor setting.}

\cvachievement{\faPlug}{Occupancy detection}{At the institute for Energy Informatics, based on multiple datasources (camera-feeds from every building entry, individual CO2-, Water-flow- , humidity- and electricity sensors in room every room), I assited a PhD student in developing a deep neural network that would extract and provide information of how many people were in the building at any given time, there location and try to predict the context/activitites of the occupancs}

\cvachievement{\faPlug}{Motion sensor}{In a 4-month semester project, a team and I developed a sensor that registered people walking on a stair. Through the use of an Arduino, data would be collected on a server.}

\cvachievement{\faWifi}{Wifi Fingerprinting}{Through the use of WiFi sniffing and statistical machine learning, in collaboration with a team, we dynamically built models of buildings and estimated the location of the sniffing phone.}


%\cvachievement{\faLeaf}{Image Recognition of Whales}{Together in a team, we started building a system that would recognize individual North Atlantic Right Whales from images, to help a group of marine biologists with tracking the species.}
\cvachievement{\faPlug}{GIS and power-grid}{At Powel, i worked with topological analysis' of the nation-wide electricity grid, mostly for fault detection, but also briefly for risk assesments.}


\cvachievement{\faCode}{Domain specific languages for building dashboard wep applications}{In order to deal with the high requirements of customizable dashboard applications for data exploration and visualization, a fellow student and I developed a prototype DSL for building custom dashboard applications}


\cvachievement{\faPaintBrush}{Augmented spray can}{By augmenting the physical surroundings through a phone, together in a team, we turned a smart phone into a spray can, where everyone could \emph{tag} everything everywhere}

%\cvachievement{\faHeartbeat}{Pill Dispencer}{Together with an interdisciplinary team, we developed a prototype of a pill dispensing box that would keep track of the medicine in the box as well as dispense the right medicine at the right time}


%{\faHeartbeat}{Common Diabetic}{Is a project that sat out to help people with diabetes through a Android app that helps the individual keeping track of medication}

%\cvachievement{\faChild}{Platform for teaching children}{In collaboration with the school of Søhus, a team and I developed and tested a prototype platform that can be used in schools to teach children}